### 2022-06-09 manuscript.tex
Merge pull request #226 from SORTEE-Github-Hackathon/RCO-reorder-box-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/55dfe2ab70354dd7be425790d6bcbeb459fbb92e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/55dfe2ab70354dd7be425790d6bcbeb459fbb92e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466364113

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f8258b509eed4946bfc21d796eab05bbae47d1d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f8258b509eed4946bfc21d796eab05bbae47d1d}{SORTEE-Github-Hackathon/manuscript@6f8258b}
on June 9, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/55dfe2ab70354dd7be425790d6bcbeb459fbb92e/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/55dfe2ab70354dd7be425790d6bcbeb459fbb92e}{SORTEE-Github-Hackathon/manuscript@55dfe2a}
on June 9, 2022.
